Dependent Object Types

### 2012-08-06 article.tex
fix typo
statement of subst lemma

Because $t_2$ reduces to a value $t_2'$ starting in store $s$, it
should also reduce to a value $v_2$ in the same number of steps
starting in store $s_1$, since $s_1$ includes $s$. So let $\reductionl
{t_2} {s_1} {v_2} {s_{12}} {j_2}$ with $v_2 \in \relv {k-j_2-1}
{\Gamma_{12}} s_{12}$.

@@

By the substitution lemma, ${\subst {v_2} {x_i} {t_i}} \in \rele
{k-\max(j_1,j_2)-1} {\Gamma_{12}} {s_{12}} {T}$. Supposing,
$\reductionl {\subst {v_2} {x_i} {t_i}} {s_{12}} {t'} {s'} {j_3}$,
with $j_1 + j_2 + j_3 + 1 = k$, this completes the case by
monotonicity of $\mathcal{V}$.

@@

\todo{statement and proof}

>>>>

Because $t_2$ reduces to a value $t_2'$ starting in store $s$, it
should also reduce to a value $v_2$ in the same number of steps
starting in store $s_1$, since $s_1$ includes $s$. So let $\reductionl
{t_2} {s_1} {v_2} {s_{12}} {j_2}$ with $v_2 \in \relv {k-j_2-1}
{\Gamma_{12}} {s_{12}} {T_2}$.

@@

By the substitution lemma, ${\subst {v_2} {x_i} {t_i}} \in \rele
{k-\max(j_1,j_2)-2} {\Gamma_{12}} {s_{12}} {T}$. Supposing,
$\reductionl {\subst {v_2} {x_i} {t_i}} {s_{12}} {t'} {s'} {j_3}$,
with $j_1 + j_2 + j_3 + 1 = j$, this completes the case, eventually by
monotonicity of $\mathcal{V}$.

@@

The substitution lemma states that if $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {T_2}$ and $t \in \rele {k_1} {\Gamma_1
  \envplus{{x_i} : S}} {s_1} T$ and $\Gamma \ts {T_2} \sub S$ with
$\Gamma$ included in $\Gamma_1$ and $\Gamma_{12}$ included in
$\Gamma_1$ and $s_{12}$ included in $s_1$, then $\subst {v_2} {x_i}
{t_i} \in \rele {\min(k_1,k_2)-1} {\Gamma_{12}} {s_{12}} T$.

\todo{proof}
